Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2021-11-22 edubots_surveys.Rnw
More issues addressed (also in response), refs #48

\textcolor{blue}{In this study, data collection involved two phases}
 \begin{itemize}
\item The first phase aimed to collect feedback from students about their actual
  needs \cite{MoraChatbots2021:anon}. Hence, the objective was to collect
  information about students’ preferences of tools/applications for chatting and
  messaging, how they use them in educational context, who do they like to be
  with in the class messaging groups, and their expectations of the chatbots in
  terms of assisting them during their learning process. Therefore, two surveys
  for bachelor and master degree students at the University of Granada (Spain)
  were designed and answers from more than 250 students were collected. The key
  findings of the students' surveys reveal that they prefer to use messaging
  applications, such as Telegram or WhatsApp as they are familiar to
  them. Students also expressed interest in chatbots that can assist them with
  organizing their course schedules, help them access their assignment grades
  and facilitate searching for course's resources.
\item The results of the first phase were fed into the second phase of the
  study, which focused on teachers’ opinions about using chatbots and messaging
  applications in classes. This is what is going to be presented in this paper.
\end{itemize}

Initially, a single survey was developed for this purpose and responses from 300
higher education teachers were collected and analysed.  The responses' analysis
entailed the creation of a second survey to which 200 teachers' responses were
collected. The questions of the second survey focussed on discussing teachers'
needs, opinions and preferences of the development of future technology-enhanced
tools and its potential impact on educational institutions’ policies. Therefore,
this paper investigated the following research questions:

>>>>

\textcolor{blue}{In this study, data collection involved two phases:}
 \begin{itemize}
\item The first phase aimed to collect feedback from students about their actual
  needs \cite{MoraChatbots2021:anon}. Hence, the objective was to collect
  information about students’ preferences of tools/applications for chatting and
  messaging, how they use them in educational context, who do they like to be
  with in the class messaging groups, and their expectations of the chatbots in
  terms of assisting them during their learning process. Therefore, two surveys
  for bachelor and master degree students at the University of Granada (Spain)
  were designed and answers from more than 250 students were collected. The key
  findings of the students' surveys reveal that they prefer to use messaging
  applications, such as Telegram or WhatsApp as they are familiar to
  them. Students also expressed interest in chatbots that can assist them with
  organizing their course schedules, help them access their assignment grades
  and facilitate searching for course's resources.
\item The results of the first phase were fed into the second phase of the
  study, which focused on teachers’ opinions about using chatbots and messaging
  applications in classes. This is what is going to be presented in this paper.
\end{itemize}

Initially, a single survey was developed for this purpose and responses from 300
higher education teachers were collected and analysed\textcolor{blue}{; this will be explained more fully in the corresponding section}.  The responses' analysis
entailed the creation of a second survey to which 200 teachers' responses were
collected\textcolor{blue}{, with the methodology and collective characteristics that will be explained below}. The questions of the second survey focussed on discussing teachers'
needs, opinions and preferences of the development of future technology-enhanced
tools and its potential impact on educational institutions’ policies. Therefore,
this paper investigated the following research questions:
